Data Management \\ and LSST Special Programs

### 2018-07-23 DMTN-065.tex
added LSE-61 flow-down statements
added non-sidereal tracked image processing statements

\setDocAbstract{This document provides an in-depth description of the role of the LSST Project in preparing software and providing computational resources to process the data from Special Programs (deep drilling fields and/or mini-surveys). The main target audience is the LSST Data Management (DM) team, but members of the community who are preparing white papers on science-driven observing strategies may also find this document useful. The potential diversity of data from Special Programs is summarized, including boundaries imposed by technical limitations of the LSST hardware. The capability of the planned Data Management system to processes this diversity of Special Programs data is the main focus of this document. Case studies are provided as examples of how the LSST software and/or user-generated pipelines may be combined to process the data from Special Programs.}

@@

@@

\subsubsection{Exposure Times}

@@

>>>>

\setDocAbstract{This document provides an in-depth description of the role of the LSST Project in preparing software and providing computational resources to process the data from Special Programs (deep drilling fields and/or mini-surveys). The plans and description in this document flow down from the requirements in \citeds{LSE-61} regarding processing for Special Programs. The main target audience is the LSST Data Management (DM) team, but members of the community who are preparing white papers on science-driven observing strategies may also find this document useful. The potential diversity of data from Special Programs is summarized, including boundaries imposed by technical limitations of the LSST hardware. The capability of the planned Data Management system to processes this diversity of Special Programs data is the main focus of this document. Case studies are provided as examples of how the LSST software and/or user-generated pipelines may be combined to process the data from Special Programs.}

@@

{\bf Telescope Tracking --} The requirement that the LSST system be able to perform non-sidereal tracking is set by OSS-REQ-0380 in \citeds{LSE-30}. This capability will include angular rates of up to $220$ arcseconds per second in both azimuth and elevation.

@@

\subsubsection{Exposure Times}\label{sssec:dmplans_NSV_expt}

@@

\subsubsection{Twilight Images with a Bright Background}

Images obtained during twilight for scientific purposes are also likely to have shorter exposure times, and so the issues described in Section \ref{sssec:dmplans_NSV_expt} also apply here. Whether or not bright-background images can (or shall) be fully processed -- reduced, calibrated, background-subtracted, and delivered with astrometric and photometric solutions -- or whether this will require a User-Generated pipeline, is TBD (see also the example in Section \ref{ssec:SPCS_Twilight}). This may depend on the exposure time and the number of stars available in the image.

\subsubsection{Images Obtained with Non-Sidereal Tracking}

Non-sidereal tracking leads to images in which stars are streaked, but the moving object appears as a point source. Full processing -- providing reduced, calibrated, background-subtracted images that are delivered with astrometric and photometric solutions -- of these images is beyond the scope of the DM pipelines as it would require the development of new algorithms, and will need to be done as a User-Generated pipeline. The first steps of such a pipeline, such as Instrument Signature Removal, will probably be possible to achieve by reconfiguring the relevant DM software tasks.
